BMI-manuscript

### 2020-11-09 manuscript/manuscript.Rmd
update

---
title: "BMI-manuscript"
output: 
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
---
\section{introduction}
Body Mass Idex (BMI) playes an important rule in predicting heart disease risk. BMI     
 .
[@van2012estimating]
\section{methode}
From the figure we see ...

>>>>

---
title: "BMI-manuscript"
output: 
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
---
\section{introduction}

Body Mass Index (BMI) plays an important rule in predicting heart disease risk[@katbody]. Our goal is to compare 90th quatile regrission for BMI in Diabtese and prediabtes population.

\section{Quantile regression}
Quantile regression is an important tool used to regress the dependent variable with high variance over the independent variables.The independent variabeles are Gender, Age, race, and statin use.

For a random variable $X$, the comulative distrubution function (CDF) is $$F(X)=P(X\leq x)$$, and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I(u<0))$$  
[@koenker2005]. The expected loss function is defined by
\begin{equation}
E\rho_{\tau}(X-\hat{x})=
\end{equation}

Least square method solve $$ \underset{\mu}{\text{min}}\sum_{i=1}^n(y_i-\mu)^2$$

\section{methods}

prevalence and incidence as a function
of age (18 – 84 years in 1-year
intervals), race/ethnicity (non-Hispanic
white, non-Hispanic black, Hispanic, or
other), sex, and BMI (underweight,
 18.5 kg/m2; normal weight, 18.5 to
 25 kg/m2; overweight, 25 to 30 kg/
m2; obese, 30 to 35 kg/m2; and very
From the figure we see

#Data
 The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES]. The data has

### 2020-11-09 manuscript/manuscript.tex
update

Body Mass Idex (BMI) playes an important rule in predicting heart
disease risk. BMI\\
. (Van de Kassteele et al. 2012) \section{methode} From the figure we
see \ldots{}

@@

\hypertarget{refs}{}
\hypertarget{ref-van2012estimating}{}
Van de Kassteele, Jan, RT Hoogenveen, PM Engelfriet, PHM Van Baal, and
HC Boshuizen. 2012. ``Estimating Net Transition Probabilities from
Cross-Sectional Data with Application to Risk Factors in Chronic Disease
Modeling.'' \emph{Statistics in Medicine} 31 (6). Wiley Online Library:
533--43.

>>>>

Body Mass Index (BMI) plays an important rule in predicting heart
disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90th
quatile regrission for BMI in Diabtese and prediabtes population.

(Van de Kassteele et al. 2012)

\section{methods}

prevalence and incidence as a function of age (18 -- 84 years in 1-year
intervals), race/ethnicity (non-Hispanic white, non-Hispanic black,
Hispanic, or other), sex, and BMI (underweight, 18.5 kg/m2; normal
weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/ m2; obese, 30 to 35
kg/m2; and very From the figure we see

\section{Quantile regression}

Quantile regression is an important tool used to regress the dependent
variable with high variance over the independent variables.

For a random variable \(X\), the comulative distrubution function (CDF)
is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\)

\section{Data}\label{data}

The data used in this study is National Health and Nutrition Examination
Survey data (NHANES)(Disease Control and (CDC) 2018)

@@

\hypertarget{refs}{}
\hypertarget{ref-NHANES}{}
Disease Control, Centers for, and Prevention (CDC). 2018. ``National
Health and Nutrition Examination Survey Data (Nhanes.''

\hypertarget{ref-katbody}{}
Katzmarzyk, Peter T, Bruce A Reeder, Susan Elliott, Michel R Joffres,
Punam Pahwa, Kim D Raine, Susan A Kirkland, and Gilles Paradis. 2012.
``Body Mass Index and Risk of Cardiovascular Disease, Cancer and
All-Cause Mortality.'' \emph{Canadian Journal of Public Health} 103 (2).
Springer: 147--51.

\hypertarget{ref-van2012estimating}{}
Van de Kassteele, Jan, RT Hoogenveen, PM Engelfriet, PHM Van Baal, and
HC Boshuizen. 2012. ``Estimating Net Transition Probabilities from
Cross-Sectional Data with Application to Risk Factors in Chronic Disease
Modeling.'' \emph{Statistics in Medicine} 31 (6). Wiley Online Library:
533--43.
